Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-22 ms.tex
made one pass at cleaning up intro and abstract

Based on the \PLANCK~2015 data release maps \citep{planck2015}, we present a 
thermal dust emission analysis analogous to that of \cite{meisner15}. We 
isolate thermal dust emission in the \PLANCK~2015 frequency maps, and present 
full-sky models of the unpolarized thermal dust emission using several 
paremeterizations of the dust spectrum, including single modified blackbody and
two-component models. The qualitative conclusions of \cite{meisner15} remain 
unchanged. In particular, zodiacal light still represents the dominant 
systematic problem on large angular scales, and the cosmic infrared background 
anisotropy remains the dominant systematic problem on small angular scales.

@@

% mention the existing dust data products, say they're all very useful for
%     many purposes
Several full-sky data products currently exist for predicting emission and/or
extinction by interstellar dust. For many years, the 
\citet[hereafter SFD]{SFD} dust map has been the industry standard for 
predicting Galactic reddening. The SFD reddening predictions rely on the
\IRAS~100$\mu$m dust emission map as a $6.1'$ FWHM template for dust optical 
depth, after modulating the emission by a $1.3^{\circ}$ FWHM temperature 
correction based on the DIRBE 140$\mu$m/240$\mu$m ratio, assuming the dust
emits as a $\beta$=2 modified blackbody (MBB). \citet[henceforth FDS99]{FDS99} 
combined the \IRAS/DIRBE data sets used by SFD with the FIRAS \citep{firas} 
dust spectra from 100-3000 GHz to extrapolate thermal dust emission from 
\IRAS~wavelengths to CMB frequencies. FDS99 found that no single MBB could
adequately fit the relatively sharp peak of the dust spectral energy 
distribution (SED) while also capturing the spectrum's flattening toward
millimeter wavelengths. FDS99 therefore fit the dust SED with a linear 
combination of two MBBs, which can be thought of as representing two 
distinct grain species in equilibrium with the same ISRF.

Both SFD/FDS99 dust temperature maps are limited to $1.3^{\circ}$ resolution 
due to their reliance on DIRBE to constrain the dust SED shape. \PLANCK's 
combination of excellent sensitivity and resolution on the Rayleigh-Jeans
side of the dust spectrum's peak allow for the construction of a full-sky dust 
temperature with near-\IRAS~angular resolution. Multiple \PLANCK-based full-sky
thermal dust model are presently available. \cite{planckdust} modeled the
\PLANCK~based dust SED from 353-3000 GHz using a single MBB model in which
beta is allowed to vary continuously at $0.5^{\circ}$ resolution. 
\cite{meisner15} applied the FDS99 two-component model to the \PLANCK~based
dust SED from 100-3000 GHz, finding that two MBBs provided a significantly
better fit than a single MBB over this expanded frequency range.

@@

Even with the enhanced temperature resolution afforded by \PLANCK, 
systematic problems with both of these recent \PLANCK~based thermal dust 
emission models still remain. Further, no thermal dust emission model yet
exists based on the \PLANCK~2015 data release. On large angular scales, 
imperfect zodical light corrections lead to the dominant systematic problem
in resulting \PLANCK~based reddening predictions \citep{meisner15}. The cosmic
infrared background anisotropies (CIBA) account for the majority of 
small-scale temperature and optical depth variation at high Galactic latitude.
Here we present an update to the analysis of \cite{meisner15}, and create the 
first ever 100-3000 GHz unpolarized thermal dust emission model based on the 
\PLANCK~2015 data release.
%But none of these are yet perfect. Mention CIBA and zodi as examples from
%Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
%exists at all.

>>>>

Based on the \PLANCK~2015 data release maps \citep{planck2015}, we present a 
thermal dust emission analysis analogous to that of \cite{meisner15}. We 
isolate thermal dust emission in the \PLANCK~2015 frequency maps, and present 
full-sky models of the unpolarized thermal dust emission from 100 to 3000 GHz
using several paremeterizations of the dust spectrum, including two-component 
and single modified blackbody models. The qualitative conclusions of 
\cite{meisner15} remain unchanged. In particular, zodiacal light still 
represents the dominant systematic problem on large angular scales, and the 
cosmic infrared background anisotropy remains the dominant systematic problem 
on small angular scales.

@@

% mention the existing dust data products, say they're all very useful for
%     many purposes
Several full-sky data products currently exist for predicting emission and/or
extinction by interstellar dust. For many years, the 
\citet[hereafter SFD]{SFD} dust map has been the industry standard for 
predicting Galactic reddening. The SFD reddening predictions rely on the
\IRAS~100$\mu$m dust emission map as a $6.1'$ FWHM template for dust optical 
depth, having modulated this emission by a $1.3^{\circ}$ FWHM temperature 
correction based on the DIRBE 140$\mu$m/240$\mu$m ratio, assuming the dust
emits as a $\beta$=2 modified blackbody (MBB). \citet[henceforth FDS99]{FDS99} 
combined the \IRAS/DIRBE data sets used by SFD with the FIRAS \citep{firas} 
dust spectra from 100-3000 GHz to extrapolate thermal dust emission from 
\IRAS~wavelengths to CMB frequencies. FDS99 found that no single MBB could
adequately fit the relatively sharp peak of the dust spectral energy 
distribution (SED) while also capturing the spectrum's flattening toward
millimeter wavelengths. FDS99 therefore fit the dust SED with a linear 
combination of two MBBs, which can be thought of as representing two 
distinct grain species in equilibrium with the same ISRF.

Both SFD/FDS99 dust temperature maps are limited to $1.3^{\circ}$ resolution 
due to their reliance on DIRBE to constrain the dust SED shape. \PLANCK's 
combination of excellent sensitivity and resolution on the Rayleigh-Jeans
side of the dust spectrum's peak allow for the construction of a full-sky dust 
temperature map with near-\IRAS~angular resolution. Multiple \PLANCK-based 
full-sky thermal dust models are presently available. \cite{planckdust} modeled
the \PLANCK-based dust SED from 353-3000 GHz using a single MBB model in which
$\beta$ is allowed to vary continuously at $0.5^{\circ}$ resolution. 
\cite{meisner15} applied the FDS99 two-component model to the \PLANCK~based
dust SED from 100-3000 GHz, finding that two MBBs provided a significantly
better fit than a single MBB over this expanded frequency range.

@@

Even with the enhanced temperature resolution afforded by \PLANCK, 
systematic problems with both of these recent \PLANCK~based thermal dust 
emission models still remain. Further, no thermal dust emission model yet
exists based on the \PLANCK~2015 data release. On large angular scales, 
imperfect zodical light corrections lead to the dominant systematic problem
in \PLANCK-based reddening predictions \citep{meisner15}. The cosmic infrared 
background anisotropies (CIBA) account for the majority of small-scale 
temperature and optical depth variation at high Galactic latitude. Here we 
present an update to the analysis of \cite{meisner15}, and create the first 
ever 100-3000 GHz unpolarized thermal dust emission model based on the 
\PLANCK~2015 data release.
%But none of these are yet perfect. Mention CIBA and zodi as examples from
%Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
%exists at all.
